What makes musicians infer teaching intentions?

### 2022-03-14 paper/manuscript.tex
first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

\abstract{
Perceiving pedagogical intentions is vital when learning skills from others. Our previous research demonstrated that expert pianists systematically modulated their sound so as to teach musical expressive techniques such as articulation and dynamics. For example, pianists played slower and exaggerated each technique when they had an intention to teach. Here we investigated whether the modulations that expert pianists produce when they intend to teach are also perceived by listeners as conveying pedagogical intentions. In the current study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented. They were asked to judge whether each recording was produced to teach the designated expressive technique or not. We quantified recordings with regard to tempo, articulation and dynamics. We performed correlation and multiple regression analysis to investigate which features of piano performance made musicians infer teaching intention. The findings in Experiment 1 with a simple musical scale demonstrated that slower tempo contributed to musicians' judgments as teaching regardless of the techniques. Moreover, performances with exaggeration for each technique (e.g., longer legato, shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching. Experiment 2 aimed to replicate the findings of Experiment 1 with a more naturalistic piece. We only replicated the findings related to dynamics (in particular, larger contrast between forte and piano). Taken together, loudness (dynamics) seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece. Also, typical pedagogical behaviour such as slowing down may not be necessarily perceived as teaching performance when learning complex skills such as artistic expression.
}

@@

In pedagogical settings where teachers are supposed to convey useful information to learners, it has been found that teachers often modulate their behaviour for teaching purposes. For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills (e.g., Brand, Baldwin, \& Ashburn, 2002; Kuhl, 2004). Also, some studies have revealed that even towards adult learners, people modulated their speech and action in the similar way as they did for infants (McEllin, Knoblich, \& Sebanz, 2017; Uther, Knoll, \& Burnham, 2007). Moreover, McEllin, Sebanz, and Knoblich (2018) demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements). These findings suggest that experts modified their speech and action to send teaching intentions and that novices could successfully perceive the intentions.

Tominaga, Knoblich \& Sebanz (\emph{submitted}) extended this line of research to expertise transmission where skills to be acquired are complex such as artistic expression. Based on the assumption that expert pianists are very good at controlling and modulating their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists could successfully modulate their performance by playing slower or exaggerating relevant aspects of the performance (e.g., producing shorter staccato or making a larger contrast between forte and piano) to teach musical expressive techniques. Therefore, it seems that even in the domain of expertise, experts exhibit general pedagogical behaviours to communicate with their potential learners.

Furthermore, some research in the field of action expertise suggest that motor simulation (i.e., using one's own motor systems to simulate an action) plays a key role to understand observed actions. For example, expert basketball players were better at predicting the outcome of a free shot compared to expert observers (coaches or sports journalists) and novices (Aglioti, Cesari, Romani, \& Urgesi, 2008). Also, it was found that deceptive intentions of fake basketball passes were detected from non-verbal bodily cues only by expert basketball players (Sebanz \& Shiffrar, 2009). Taken together, people seem to be able to infer informative intentions by observing actions accurately if they have enough expertise to simulate the actions.

In the domain of music, musical emotion is often communicated by sound alone and listeners seem to be able to infer performers' intended emotions only by listening to recorded performances (e.g., Akkermans et al., 2019; Gabrielsson \& Juslin, 1996). It has been known that musicians are generally more accurate to decode emotions from performances (Battcock \& Schutz, 2021; Lima \& Castro, 2011). Repp and Knoblich (2004) also found that expert pianists could distinguish their own performance from others' performances by listening to recordings. These results suggest that musical expertise may enable people identify and infer intentions accurately by using their own motor resources.

Here we investigated whether the modulations that expert pianists made when they intended to teach were also perceived by listeners as conveying pedagogical intentions. We quantified recordings with regard to tempo, articulation and dynamics and examined which features of piano performance made musicians infer teaching intentions. We performed correlation and multiple regression analysis to investigate relationships between performance features of a recording and how likely people think the recording was produced for teaching purposes. Various piano recordings were collected from our previous experiments (Tominaga et al., \emph{submitted}). The recordings were performed by various pianists multiple times, therefore the recordings contained many variations in terms of timing, articulation and dynamics. In the current study, we asked musically trained participants to judge which each recording was performed for teaching purposes. If performers' intentions are successfully communicated with learners, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions. We examined which features of piano performance were correlated with participants judgments as ``teaching''. We conducted Experiment 1 with a simple musical scale and Experiment 2 with a more naturalistic piece of music to replicate the findings from Experiment 1.

@@

We selected stimuli from our previous experiments (Tominaga et al., \emph{submitted}). Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files. Multiple pianists played one piece of music with a musical expressive techniques of either articulation (\emph{Figure \ref{fig:stim1}}, A) or dynamics (\emph{Figure \ref{fig:stim1}}, B). Articulation refers to the smoothness of sound, which is comprised of legato and staccato. Legato indicates smooth and connected sound whereas staccato indicates sharp and separate sound. Dynamics refers to the loudness of sound, which is comprised of forte and piano. Forte indicates loud sound while piano indicates soft sound. The piece was taken from ``A Dozen a Day - Play with Ease in Many Keys'' by Edna-Mae Burnam and modified for the experiment. The stimuli were performed around 80 quarter-beats per minute.

In Tominaga et al., (\emph{submitted}), participants were asked to perform the piece with either articulation or dynamics in two different conditions. In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson). In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert). In total, we obtained 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition.

For the current experiment, 96 recordings were chosen from the valid performances in Tominaga et al.~(\emph{submitted}; Experiment 1). We randomly sampled 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition. It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances.

@@

@@

@@

In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted. Statistical model assumptions were tested using the \emph{performance} R package (Lüdecke, Ben-Shachar, Patil, Waggoner, \& Makowski, 2021) and all assumptions were met. Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis}).

@@

The data analysis was identical to Experiment 1. Only the 8th notes with expressive notations were included for data analysis. As a result, only one 8th note in the 4th measure without any expression was not included.

@@

@@

Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; \emph{r(34)} = .25, \emph{p} = 0.15, Dynamics; \emph{r(34)} = .39, \emph{p} = 0.02, \emph{Figure \ref{fig:ioi-2}}). The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.080). A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (\emph{r(34)} = .29, \emph{p} = 0.091).

@@

For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (\emph{r(34)} = -.11, \emph{p} = 0.52). However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = 0.034), suggesting that performances with louder staccato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).

@@

As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-2}}, right). Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(34)} = -.75, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} 0.001). The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; \emph{p} = 0.850, Piano to Forte; \emph{p} = 0.008). Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r(34)} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r(34)} = .57, \emph{p} \textless{} 0.001).

@@

As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching. Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis} in Experiment 1).

@@

@@

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-aglioti_2008}{}}%
Aglioti, S. M., Cesari, P., Romani, M., \& Urgesi, C. (2008). Action anticipation and motor resonance in elite basketball players. \emph{Nature Neuroscience}, \emph{11}(9), 1109--1116. \url{https://doi.org/10.1038/nn.2182}

\leavevmode\vadjust pre{\hypertarget{ref-akkermans_2019}{}}%
Akkermans, J., Schapiro, R., Müllensiefen, D., Jakubowski, K., Shanahan, D., Baker, D., \ldots{} Frieler, K. (2019). Decoding emotions in expressive music performances: {A} multi-lab replication and extension study. \emph{Cognition and Emotion}, \emph{33}(6), 1099--1118. \url{https://doi.org/10.1080/02699931.2018.1541312}

\leavevmode\vadjust pre{\hypertarget{ref-battcock_2021}{}}%
Battcock, A., \& Schutz, M. (2021). Emotion and expertise: How listeners with formal music training use cues to perceive emotion. \emph{Psychological Research}. \url{https://doi.org/10.1007/s00426-020-01467-1}

@@

\leavevmode\vadjust pre{\hypertarget{ref-kuhl_2004}{}}%
Kuhl, P. K. (2004). Early language acquisition: Cracking the speech code. \emph{Nature Reviews Neuroscience}, \emph{5}(11), 831--843. \url{https://doi.org/10.1038/nrn1533}

\leavevmode\vadjust pre{\hypertarget{ref-lima_2011}{}}%
Lima, C. F., \& Castro, S. L. (2011). Speaking to the trained ear: Musical expertise enhances the recognition of emotions in speech prosody. \emph{Emotion}, \emph{11}(5), 1021--1031. \url{https://doi.org/10.1037/a0024521}

@@

\leavevmode\vadjust pre{\hypertarget{ref-repp_2004}{}}%
Repp, B. H., \& Knoblich, G. (2004). Perceiving {Action Identity}: {How Pianists Recognize Their Own Performances}. \emph{Psychol Sci}, \emph{15}(9), 604--609. \url{https://doi.org/10.1111/j.0956-7976.2004.00727.x}

\leavevmode\vadjust pre{\hypertarget{ref-sebanz_2009}{}}%
Sebanz, N., \& Shiffrar, M. (2009). Detecting deception in a bluffing body: {The} role of expertise. \emph{Psychonomic Bulletin and Review}, \emph{16}(1), 170--175. \url{https://doi.org/10.3758/PBR.16.1.170}

>>>>

\abstract{
Perceiving pedagogical intentions is vital when learning skills from others. Our previous research demonstrated that expert pianists systematically modulated their sound so as to teach musical expressive techniques such as articulation and dynamics. For example, pianists played slower and exaggerated each technique when they had an intention to teach. Here we investigated whether the modulations that expert pianists produce when they intend to teach are also perceived by listeners as conveying pedagogical intentions. In the current study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented. Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings) whereas the other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings). Participants were asked to judge whether each recording was produced for teaching purposes or not. We calculated the accuracy of participants' judgments to investigate whether they could distinguish teaching recordings from performing recordings. Also, recordings were quantified with regard to tempo, articulation and dynamic so that we could perform correlation and multiple regression analysis to investigate which features of piano performance made musicians infer teaching intentions. The findings in Experiment 1 with a simple musical scale demonstrated that the accuracy of musicians' judgments was significantly above chance. Also, it was found that slower tempo contributed to musicians' judgments as teaching regardless of the techniques. Moreover, performances with exaggeration for each technique (e.g., longer legato, shorter staccato, larger contrast between forte and piano) were more likely to be judged as teaching. Experiment 2 aimed to replicate the findings of Experiment 1 with a more naturalistic piece. As Experiment 1, the accuracy of musicians' judgments was significantly above chance. However, we only replicated that performances with exaggerated dynamics (in particular, larger contrast between forte and piano) were more likely to be judged as teaching. Taken together, loudness (dynamics) seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece. Also, typical pedagogical behaviour such as slowing down may not be necessarily perceived as teaching performance when learning complex skills such as artistic expression.
}

@@

In pedagogical settings where teachers are supposed to convey useful information to learners, it has been found that teachers often modulate their behaviour for teaching purposes. For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills (e.g., Brand, Baldwin, \& Ashburn, 2002; Saint-Georges et al., 2013). Also, some studies have revealed that even towards adult learners, people modulated their speech and action in the similar way as they did for infants (McEllin, Knoblich, \& Sebanz, 2017; Uther, Knoll, \& Burnham, 2007). Moreover, McEllin, Sebanz, and Knoblich (2018) demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements). These findings suggest that experts modified their speech and action to send teaching intentions and that novices could successfully perceive the intentions.

Tominaga, Knoblich \& Sebanz (\emph{submitted}) extended this line of research to expertise transmission where skills to be acquired are complex such as artistic expression. Based on the assumption that expert pianists are skilled at controlling their sound to communicate, we investigated how expert pianists could modulate their performance when they were intending to teach musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists could successfully modulate their performance by playing slower or exaggerating relevant aspects of the performance (e.g., producing shorter staccato or making a larger contrast between forte and piano) to teach musical expressive techniques. Therefore, it seems that even in the domain of expertise, experts exhibit general pedagogical behaviours to communicate with their potential learners.

Here we investigated whether the modulations that expert pianists made when they intended to teach were also perceived by listeners as conveying pedagogical intentions. We assumed that listeners would be able to infer intentions only by listening to recordings because some research revealed that musical emotion is often communicated by sound alone and that listeners seem to be able to infer performers' intended emotions only by listening to recorded performances (e.g., Akkermans et al., 2019; Gabrielsson \& Juslin, 1996). In the present study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented. They were asked to judge whether each recording was produced for teaching purposes or not. Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings) whereas the other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings). First, we calculated the accuracy of participants' judgments to examine whether they could distinguish teaching recordings from performing recordings. Furthermore, recordings were quantified with regard to tempo, articulation and dynamic. We performed correlation and multiple regression analysis to examine relationships between performance features of the recordings and how likely people think the recordings were produced for teaching purposes. Various piano recordings were collected from our previous experiments (Tominaga et al., \emph{submitted}). The recordings were performed by various pianists multiple times, therefore the recordings contained many variations in terms of timing, articulation and dynamics.

If performers' intentions are successfully communicated with learners, musicians would be able to distinguish teaching recordings from performing recordings. Moreover, pedagogical behavioural features in our previous experiments such as slower demonstration and exaggerated performance should be identified and used to infer teaching intentions. We examined which features of piano performance were correlated with participants judgments as teaching. We conducted Experiment 1 with a simple musical scale and Experiment 2 with a more naturalistic piece of music to replicate the findings from Experiment 1.

@@

We selected stimuli from our previous experiments (Tominaga et al., \emph{submitted}). Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files. Multiple pianists played one piece of music with a musical expressive technique of either articulation (\emph{Figure \ref{fig:stim1}}, A) or dynamics (\emph{Figure \ref{fig:stim1}}, B). Articulation refers to the smoothness of sound, which is comprised of legato and staccato. Legato indicates smooth and connected sound whereas staccato indicates sharp and separate sound. Dynamics refers to the loudness of sound, which is comprised of forte and piano. Forte indicates loud sound while piano indicates soft sound. The piece was taken from ``A Dozen a Day - Play with Ease in Many Keys'' by Edna-Mae Burnam and modified for the experiment. The stimuli were performed around 80 quarter-beats per minute.

In Tominaga et al., (\emph{submitted}), participants were asked to perform the piece with either articulation or dynamics in two different conditions. In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson). In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert). In Tominaga et al.~(\emph{submitted}; Experiment 1), there were 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition. For the current experiment, 96 recordings were chosen from the valid performances. We randomly sampled 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition. It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances.

@@

\hypertarget{accuracy}{%
\subsubsection{Accuracy}\label{accuracy}}

First, we examined whether participants could accurately distinguish the stimuli chosen from the teaching condition in Tominaga et al., (\emph{submitted}; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (\emph{submitted}; Experiment 1) as performing. We compared how accurate participants were against the chance level (50\%). The correct responses were either pressing the yes button when listening to the teaching recordings or pressing the no button when listening to the performing recordings. The incorrect responses were either pressing the yes button when listening to the performing recordings or pressing the no button when listening to the teaching recordings.

\hypertarget{correlation-and-multiple-regression}{%
\subsubsection{Correlation and multiple regression}\label{correlation-and-multiple-regression}}

@@

\hypertarget{accuracy-1}{%
\subsection{Accuracy}\label{accuracy-1}}

A one sample \emph{t}-test was performed to compare the accuracy of participants' judgments against the chance level (50\%). The mean percentage of correct answers {[}\emph{M} = 52.7, \emph{SD} = 4.90{]} was significantly higher than chance (\emph{t}(19) = 2.47, \emph{p} = 0.02, cohen's \emph{d} = 0.55).

We also performed a one sample \emph{t}-test for each technique separately. For articulation, the mean percentage of correct answers {[}\emph{M} = 50.2, \emph{SD} = 6.55{]} was not significantly different from chance (\emph{t}(19) = 0.14, \emph{p} = 0.89, cohen's \emph{d} = 0.03). For dynamics, the mean percentage of correct answers {[}\emph{M} = 55.2, \emph{SD} = 7.81{]} was significantly higher than chance (\emph{t}(19) = 2.98, \emph{p} = 0.01, cohen's \emph{d} = 0.67). A paired \emph{t}-test revealed that there was a significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -2.12, \emph{p} = 0.05, cohen's \emph{d} = -0.69), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.

@@

In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted. Statistical model assumptions were tested using the \emph{performance} R package (Lüdecke, Ben-Shachar, Patil, Waggoner, \& Makowski, 2021) and most of the assumptions (see \emph{Supplementary Material} for details) were met. Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis}).

@@

The data analysis was almost identical to Experiment 1. Only the 8th notes with expressive notations were included for data analysis. As a result, only one 8th note in the 4th measure without any expression was not included.

@@

\hypertarget{accuracy-2}{%
\subsection{Accuracy}\label{accuracy-2}}

A one sample \emph{t}-test was performed to compare the accuracy of participants' judgments against the chance level (50\%). The mean percentage of correct answers {[}\emph{M} = 52.8, \emph{SD} = 4.78{]} was significantly higher than chance (\emph{t}(19) = 2.66, \emph{p} = 0.02, cohen's \emph{d} = 0.60).

We also performed a one sample \emph{t}-test for each technique separately. For articulation, the mean percentage of correct answers {[}\emph{M} = 52.4, \emph{SD} = 6.94{]} was not significantly different from chance (\emph{t}(19) = 1.52, \emph{p} = 0.14, cohen's \emph{d} = 0.34). Also for dynamics, the mean percentage of correct answers {[}\emph{M} = 53.3, \emph{SD} = 8.53{]} was not significantly different from chance (\emph{t}(19) = 1.75, \emph{p} = 0.10, cohen's \emph{d} = 0.39). A paired \emph{t}-test revealed that there was no significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -0.35, \emph{p} = 0.73, cohen's \emph{d} = -0.13).

@@

Unlike Experiment 1, there was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; \emph{r(34)} = .25, \emph{p} = 0.15, Dynamics; \emph{r(34)} = .39, \emph{p} = 0.02, \emph{Figure \ref{fig:ioi-2}}). Participants tended to identify slower performances as teaching for dynamics recordings.

However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.080). A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (\emph{r(34)} = .29, \emph{p} = 0.091), suggesting that we need to be careful about the interpretation of the relationship between the performance tempi of dynamics recordings and participants' judgments as teaching.

@@

For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (\emph{r(34)} = -.11, \emph{p} = 0.52). However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = 0.034), suggesting that performances with staccato-style piano were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).

@@

As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (\emph{Figure \ref{fig:vel-diff-2}}, right). Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; \emph{r(34)} = -.75, \emph{p} \textless{} 0.001, From Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} 0.001). The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; \emph{p} = 0.85, Piano to Forte; \emph{p} = 0.008). Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r(34)} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r(34)} = .57, \emph{p} \textless{} 0.001).

@@

As Experiment 1, we performed multiple regression analyses to further explore which feature of performance contributed the most to participants' judgments as teaching. Statistical model assumptions were tested and most of the assumptions (see \emph{Supplementary Material} for details) were met. Again, since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs.~staccato, forte vs.~piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in \emph{Data analysis} in Experiment 1).

@@

The aim of Experiment 2 was to replicate the results of Experiment 1 with a more naturalistic piece of music. However, unlike Experiment 1, tempo (IOIs) does not seem to contribute to participants' judgments as teaching. This could be that in a musically complex piece, tempo might have been considered to be one of the interpretations of music and was not used as a reliable cue to infer teaching intentions. Also, articulation (KOT) does not seem to contribute to participants' judgments as teaching. As Experiment 1, dynamics (KV) seems to be used as a reliable cue to detect the characteristic of teaching performance. We could successfully replicate that performances with larger contrast between forte and piano seem to be considered as teaching. Moreover, performances with both exaggerated forte and piano were considered to be for teaching. These consistent results suggest that loudness (dynamics) might be used as a reliable cue to infer teaching intentions regardless of the complexity of a musical piece.

Multiple regression analyses also implied that tempo feature was not a strong predictor of participants' judgments as teaching when listening to a musically complex piece. However, dynamics contrast seems to be a strong predictor of participants' judgments as teaching, especially for dynamics recordings. This finding also suggests that loudness might be a strong cue to infer pedagogical intentions even in a naturalistic piece of music.

@@

The present study investigated whether and how musician infer pedagogical intentions by listening to piano recordings. In both Experiment 1 and 2, participants were able to choose correct answers accurately more than chance (50\%). However, the results showed that the accuracy was relatively low (52.7 \% in Experiment 1; 52.8 \% in Experiment 2). This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.~(\emph{submitted}) and all the selected recordings did not exhibit the characteristics of teaching performance (e.g., slow performance, exaggeration). The reason why we randomly selected the stimuli from each condition (i.e., teaching or performing) was because all the characteristics of teaching performance (e.g., IOIs, KOT, KV) were intercorrelated and it was difficult to choose stimuli based on one single criterion. Future research should examine if musicians answer more accurately with more experimentally controlled stimuli.

In order to examine which features of piano performance make musicians infer pedagogical intentions, we performed correlation and multiple regression analysis. Across the two experiments, it was found that loudness, particularly larger contrast between forte and piano, strongly contributed to participants' judgments when listening to dynamics recordings. On the other hand, unlike what we predicted, slower performance was only considered to be for teaching in Experiment 1 where the stimuli consisted of a simple musical scale. Also, we could not find that performances with exaggerated articulation (e.g., longer legato and shorter staccato) were more likely to be judged as teaching in Experiment 2. This might suggest that some characteristics of performance are not necessarily used or reliable to infer performers' intentions when listening to musically complex pieces. It can be speculated that certain modulations are too subtle so that participants could not perceive them. Another possibility is that modulations can also be considered as one of the expressions or interpretations.

In the current study, we exclusively recruited musicians to explore our research questions. The reason why we recruited musicians only was because the concepts of articulation and dynamics seem to be difficult for those who don't play an instrument to understand in the current settings. It would be important to investigate how novices perceive and infer pedagogical intentions differently from musicians, who already have some experience in playing music.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-akkermans_2019}{}}%
Akkermans, J., Schapiro, R., Müllensiefen, D., Jakubowski, K., Shanahan, D., Baker, D., \ldots{} Frieler, K. (2019). Decoding emotions in expressive music performances: {A} multi-lab replication and extension study. \emph{Cognition and Emotion}, \emph{33}(6), 1099--1118. \url{https://doi.org/10.1080/02699931.2018.1541312}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-saint-georges_2013}{}}%
Saint-Georges, C., Chetouani, M., Cassel, R., Apicella, F., Mahdhaoui, A., Muratori, F., \ldots{} Cohen, D. (2013). Motherese in {Interaction}: {At} the {Cross-Road} of {Emotion} and {Cognition}? ({A Systematic Review}). \emph{PLOS ONE}, \emph{8}(10), e78103. \url{https://doi.org/10.1371/journal.pone.0078103}
